---
title: "Do risk preferences really matter? The case of pesticide use in agriculture"
author: "Christophe Bontemps, Douadia Bougherara, Céline Nauges"
date: "`r format(Sys.time(), '%d %B, %Y')`"

output: 
  html_document:
    code_folding: hide
    number_sections: TRUE
    theme: lumen
    highlight: tango

---

```{r setup, include=FALSE}
knitr::opts_chunk$set( message = FALSE, warning = FALSE, echo = FALSE) 

```
# Simulations framework 
## Initialization

We use some standard packages for doing the simulations. These packages can be downloaded simply by uncommenting the first lines of the next code chunk.

```{r packages}

# Uncomment the following line to install the packages if not already installed
# install.packages( c("dplyr", "ggplot2", "purrr", "spatstat.utils", "stargazer"))

#Packages used in this simulation
library(dplyr)
library(ggplot2)
library(purrr)
library(spatstat.utils) # for revcumsum
library(stargazer)

```
 
We created several functions for 
* computing utility (CRRA and CPT) and 
* for computing the optimal input use and risk premium in different cases. 
The functions are defined in a separate R file that must be loaded. 

```{r}
source("GlobalFunctions.R")
```



To account for uncertainty in the empirical analysis to follow we assume that the random shock follows a standardized normal distribution and we derive the discrete analogue of the continuous N(0,1) by considering 1,000 normally distributed $\epsilon_i$ (i=1, 2 … 1000) over a large support.

### Simulation parameters

```{r,  echo = TRUE}
# Parameters of the simulation [Numbers can be changed below]
N.eps <- 1000  
# Computing epsilons data.frame
Epsilons <- GenEpsilon(Neps = N.eps)

```

### Input simulation values

we consider possible values for $x$ varying from 1 to 400 EUR for one hectare.

```{r Epsilons,  echo = TRUE}

## Generation of simulated Xi (input) over the support [0,400] [values can be changed here]
suppmin <- 0
suppmax <- 400  # Defines the length of the support for inputs [0, suppmax]

Ns <- 400     # Number of points of the computaion grid for the integral
x <- as.data.frame(seq(from = suppmin, to = suppmax, length.out = Ns+1 ))
x<- x[-1,]  #  to avoid start at x=0

df<- data.frame(x)
df.final <- df

```

## Production function

We consider the following Just-Pope production function: 
$$ y = f(x)+ g(x)*\epsilon = c_0+ a x^\alpha + bx^\beta*\epsilon$$
with a, b $\gt 0$, $\alpha \gt 0$ , $\beta \lt 0$ and $\epsilon$ a random shock shock assumed to be of mean 0. 

### Production function parameters

The parameters of the production function (for the benchmark scenario) were chosen such that the function fits real production data from France; that is: 

```{r ProdParameters, echo = TRUE}
# Production function parameters (Benchmark) - [ values may be changed here]

c0 <- 0
a <-  15
alpha <- 0.30
b <- 30
beta <- -0.10
```

```{r}
#Text for output 
text.param.prod <-  paste0("Production function y =", ifelse(c0 == 0, "",paste(c0," + ")),
                          a," * x**", alpha, " +",b,"* x**",beta," * eps" )
```

### Profit parameters

Output is wheat and is measured in quintal (1 q = 0.1 t = 100 kg). We set the price of wheat (p) at 110 EUR/t or, equivalently, 11 EUR/q. We also definie the initial wealth, $w_0$ to be set at 500 EUR. The price of inputs is normalized to one.

```{r ProfParameters,   echo = TRUE  }
# Profit function parameters [values can be changed here]
py <- 11      # Price ratio 
w0 <- 500     # Initial wealth
```
These parameters may be changed, and  will vary in our simulations (Tables 2-5) 

```{r CompProf}
#Individual profit
df.profMat <- data.frame(mapply(function(x, y) 
  (w0 + py*(c0 +a * x^alpha + b * (x ^beta) *y) - x),
  df,Epsilons$eps))

# Computing the integral (expected profit)
df.EprofMat <- data.frame(mapply(`*` , df.profMat, Epsilons$probeps))

# Expected profit
df.final$EProf <- rowSums(df.EprofMat,  na.rm=T)
```


```{r}
#Graphics

df.MeanProfMat <-  data.frame(mapply(function(x, y) 
  (w0 + py*(c0 +a * x^alpha) - x),
  df,Epsilons$eps))

text.param.mean <-  paste("Mean production function y =", ifelse(c0 == 0, "",paste(c0,"+")),
                          a," * x**", alpha,"( \U03F5 =0)" )

# Computing the integral (expected profit)
df.EMeanProfMat <- data.frame(mapply(`*` , df.MeanProfMat, Epsilons$probeps))

# Expected profit
df.plot <- df
df.plot$MeanProf <- rowSums(df.EMeanProfMat,  na.rm=T)

i.star <- which.max(df.plot$MeanProf)
x.star  <- df.plot[i.star,"x"]
EProf.star <- df.plot[i.star, "MeanProf"]

    myalpha <- 0.8
    # Main benchmark curve
    main.plot <- ggplot(df.plot, aes(x, MeanProf) ) +
      geom_line( colour = "pink", size=2, alpha= myalpha) +
      ggtitle(label = paste("Expected profit (Initial wealth =", w0,")") ,
              subtitle =  paste(text.param.mean, ", Price ratio = ", py)) +
      coord_cartesian(ylim=c(w0, w0+1000), xlim =c(0,450)) +
      labs( x= paste("Input use (EUR/ha)")  ,
            y = "Profit (EUR)") +
      theme_minimal()
    
   main.plot + 
      geom_segment(aes(x = x.star, y = w0 + 30, 
                       xend = x.star, yend = EProf.star),
                   colour = "pink", alpha = myalpha, size = 1,
                   linetype = "dashed", data = df.plot) +
     geom_text(x= x.star + 30, y=  w0 + 30, 
               label= paste("x* =", x.star), colour ="pink")
    
    

```




# Simulation results: Expected Utility framework 

## Benchmark scenario
In Table 1 we report the optimal level of input use, the risk premium, and the certainty equivalent (all measured in EUR for one hectare) under the risk neutrality assumption (rr = 0) and under risk aversion for four different levels of the coefficient of relative risk aversion (rr = 1, 2, 3 and 4). 

```{r  LoopRisk , echo = TRUE }
# The table 1 is constructed as a single loop  
# over a list of risk aversion parameter values: [values can be changed here]
r.list <- c(0,1,2,3,4)

```

**Table 1**

```{r Table1 , include = TRUE, echo = FALSE, cache  = FALSE}
# Initialising the result's data frame 
res.CRRA<- data.frame()

# We loop on the value of the parameter representing the coefficient of relative risk aversion
for (i.r in seq_along(r.list))  {
  
  #Storing price ratio in a data frame (results) 
  res.CRRA [1, "price ratio"] <- py

  ## --  Computing the risk-neutral optimum -- ##
    df.final0 <- df    # initialization
    df.UMat0 <- map_df(df.profMat, U.CRRA, r = 0)
  
    # Computing the integral
    df.EUMat0 <-  data.frame(mapply(`*` , df.UMat0, Epsilons$probeps))
    df.final0$EU <- rowSums(df.EUMat0,  na.rm=T)
  
    # Risk neutral: Computing the index of the maximum; storing maximum Expected Utility and profit) 
    i.star0 <- which.max(df.final0$EU)
    x.star0  <- df.final0[i.star0,"x"]
    EU.star0 <- df.final0[i.star0, "EU"]
    EProf.star0 <- df.final0[i.star0, "EProf"]

  ## -- End risk-neutral case for that value of price ratio -- ##
  
  # Computation of profit for current price ratio and current risk aversion parameter 
  df.UMat <- map_df(df.profMat, U.CRRA, r = r.list[i.r])
  # Computing the integral
  df.EUMat <-  data.frame(mapply(`*` , df.UMat, Epsilons$probeps))
  df.final$EU <- rowSums(df.EUMat,  na.rm=T) 

  # Computing the index of the maximum; storing maximum Expected Utility and profit 
  i.star <- which.max(df.final$EU)
  x.star  <- df.final[i.star,"x"]
  EU.star <- df.final[i.star, "EU"]
  EProf.star <- df.final[i.star, "EProf"]
  
  # Share of input used for self-insurance (measured in percentage terms)
  delta.x <- 100*(x.star - x.star0)/x.star

  # Computing risk premium
  ## -- Defining the optimization function
    fopti.CRRA.r <- function(RP, ...){
      abs(EU.star - U.CRRA(df.final[i.star,]$EProf - RP,r = r.list[i.r]))
    }

  # CRRA solution and risk premium (grid search between -100 and 500)
  RP.sol <- optimize( fopti.CRRA.r, interval = c(-100,500), maximum = FALSE)
  RP <- round(RP.sol$minimum, digits = 3)

  ### Certainty equivalent
  CE <- df.final[i.star,"EProf"] - RP

  ## Putting results in data frame

  res.CRRA[ 1, paste0("r = ",r.list[i.r])] <- round(x.star, digits = 0)
  res.CRRA[ 2, paste0("r = ",r.list[i.r])] <-  round(delta.x, digits = 2)
  res.CRRA[ 3, paste0("r = ",r.list[i.r])] <-  round(RP, digits = 0)
  res.CRRA[ 4, paste0("r = ",r.list[i.r])] <-  round(CE, digits = 0)
  res.CRRA[ 5, paste0("r = ",r.list[i.r])] <-  round(-100*RP/EProf.star, digits = 2)
}

rownames(res.CRRA) <- c( "X*","Input change", "RP",  "CE","RP/Prof*" )

## Formatted output
stargazer(res.CRRA,
          summary = FALSE,
          title = paste("CRRA (N.eps =", N.eps,"), Initial wealth = ", w0),
          notes = paste0(text.param.prod,"  (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("Table1-", format(Sys.time(), "%Y-%m-%d")," .txt")
)

```


## Sensitivity of input use to levels of relative risk aversion and price ratios

```{r LoopPrice , echo = TRUE }
# Table 2 is constructed as a double loop  [values can be changed here]
# # First loop: 
# values considered for the price ratio, py, are: 
py.list <- c(13, 11, 9, 7)

# Inner loop : 
# The list of risk aversion parameter values is the same as in Table 1

```

**Table 2**

```{r Table2 , include = TRUE, echo = FALSE, cache = FALSE}
# Initializing data frame for results
Simu.py <- data.frame()

# Looping over price ratio 
for (j in seq_along(py.list))  {
    # Initializing temporay data frame
    res.CRRA<- data.frame()

    # Current price ratio 
    py <- py.list[j]

    #Individual profit
    df.profMat <- data.frame(mapply(function(x, y) 
      (w0 + py*(c0 + a * x^alpha + b * (x ^beta) *y) - x),
      df,Epsilons$eps))

    # Computing the integral (expected profit)
    df.EprofMat <- data.frame(mapply(`*` , df.profMat, Epsilons$probeps))

    # Expected profit
    df.final$EProf <- rowSums(df.EprofMat,  na.rm=T)
    
    # Looping over risk aversion parameter
    for (i.r in seq_along(r.list))  {
      # Storing current price ratio
      res.CRRA [1, "price ratio"] <- py

      ## --- Computing the risk-neutral optimum for that price ratio -- ##
        #Initialization
        df.final0 <- df   
        df.UMat0 <- map_df(df.profMat, U.CRRA, r = 0)
        
        # Computing the integral
        df.EUMat0 <-  data.frame(mapply(`*` , df.UMat0, Epsilons$probeps))
        df.final0$EU <- rowSums(df.EUMat0,  na.rm=T)
  
        # Computing the index of the maximum (r = 0 case)
        i.star0 <- which.max(df.final0$EU)
        x.star0  <- df.final0[i.star0,"x"]
        EU.star0 <- df.final0[i.star0, "EU"]
        EProf.star0 <- df.final0[i.star0, "EProf"]
        
      ## --- End risk-neutral case for that value of price ratio -- ##

      ## Computing for all r.list values
      df.UMat <- map_df(df.profMat, U.CRRA, r = r.list[i.r])
      
      # Computing the integral
      df.EUMat <-  data.frame(mapply(`*` , df.UMat, Epsilons$probeps))
      df.final$EU <- rowSums(df.EUMat,  na.rm=T)

      # Computing the index of the maximum; storing maximum Expected Utility and profit
      i.star <- which.max(df.final$EU)
      x.star  <- df.final[i.star,"x"]
      EU.star <- df.final[i.star, "EU"]
      EProf.star <- df.final[i.star, "EProf"]
      
      # Share of input used for self-insurance
      delta.x <- 100*(x.star - x.star0)/x.star

      # Computing the risk premium
      ## -- Defining the optimization function
        fopti.CRRA.r <- function(RP, ...){
          abs(EU.star - U.CRRA(df.final[i.star,]$EProf - RP,r = r.list[i.r]))
        }

      # CRRA solution and risk premium
      RP.sol <- optimize( fopti.CRRA.r, interval = c(-100,500), maximum = FALSE)
      RP <- round(RP.sol$minimum, digits = 3)

      ###  Certainty equivalent 
      CE <- df.final[i.star,"EProf"] - RP

      ## Putting results in table for current risk parameter and price ratio values 
      res.CRRA[ 1, paste0("r = ",r.list[i.r])] <- round(x.star, digits = 0)
      res.CRRA[ 2, paste0("r = ",r.list[i.r])] <-  round(delta.x, digits = 2)
      res.CRRA[ 3, paste0("r = ",r.list[i.r])] <-  round(RP, digits = 0)
      res.CRRA[ 4, paste0("r = ",r.list[i.r])] <-  round(-100*RP/EProf.star, digits = 2)
      res.CRRA[5, ] <- NA

      rownames(res.CRRA) <- c( "X*","Input change", "RP","RP/Prof*", " " )

    } #end loop over values of r

    # Appending the results for the next loop 
    Simu.py <-  rbind( Simu.py, res.CRRA)

}  #end loop over price ratio, py


## Formatted output
stargazer(Simu.py,
          summary = FALSE,
          title = paste("CRRA (N.eps =", N.eps,"), Initial wealth = ", w0),
          notes = paste0(text.param.prod,"  (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("Table2-", format(Sys.time(), "%Y-%m-%d")," .txt")
          )


```


## Sensitivity of input use to levels of relative risk aversion and parameters of the mean yield function

```{r LoopProd , echo = TRUE }
# Table 3 is constructed as a double loop  [values can be changed here]
# First loop: 
# Cases proposed for the mean yield function parameters:
#  Values are for a and alpha (resp.)
case.prod.f <-        data.frame(c(15, 0.20))  # Case1
case.prod.f <- cbind(case.prod.f,c(15, 0.25))  # Case2
case.prod.f <- cbind(case.prod.f,c(15, 0.30 )) # Benchmark
case.prod.f <- cbind(case.prod.f,c(10, 0.30 )) # Case4
case.prod.f <- cbind(case.prod.f,c(18, 0.30 )) # Case5
row.names(case.prod.f ) <- c("a", "alpha")

# NB: Risk function parameters are fixed to: 
b = 30
beta = -0.10

# Inner loop: 
# Values considered for the risk aversion parameter, r:
r.list <- c(0,1,2,3,4)

# Invariant parameters (in this simulation)
w0 <- 500
py <- 11
```

**Table 3**

```{r Table3 , include = TRUE, echo = FALSE, cache = FALSE}

# Initializing
Simu.prod.f <- data.frame()

# Loop on mean yield function parameters (cases)
for (j in 1:ncol(case.prod.f) )  {

  # Current production function parameters
  a = case.prod.f[1,j]
  alpha = case.prod.f[2,j]

  # Text stored for output presentation
  param.prod.f <- paste0(ifelse(c0 == 0, "",paste(c0," + ")),a,"* x**", alpha )
  param.prod.g <- paste0(b,"* x**",beta)
  text.param.prod <-  paste0("Production function y = ",param.prod.f," + ",param.prod.g,"* eps"  )
  
  # Individual profit
  df.profMat <- data.frame(mapply(function(x, y) (w0 + py*(c0 + a * x^alpha + b * (x ^beta) *y) - x),
                                  df,Epsilons$eps))

  # Computing the integral (expected profit)
  df.EprofMat <- data.frame(mapply(`*` , df.profMat, Epsilons$probeps))

  # Expected profit
  df.final$EProf <- rowSums(df.EprofMat,  na.rm=T)
  
  # Looping over risk aversion parameter
  res.CRRA<- data.frame()
  for (i.r in seq_along(r.list))  {
    res.CRRA [1, "Mean yield function"] <- paste0("f(x) = ",param.prod.f)

    ## --- Computing the risk-neutral optimum for current parameter values -- ##
      # Initialization
      df.final0 <- df    
      df.UMat0 <- map_df(df.profMat, U.CRRA, r = 0)
      
      # Computing the integral
      df.EUMat0 <-  data.frame(mapply(`*` , df.UMat0, Epsilons$probeps))
      df.final0$EU <- rowSums(df.EUMat0,  na.rm=T)
  
      # Computing the index of the maximum (r = 0 case)
      i.star0 <- which.max(df.final0$EU)
      x.star0  <- df.final0[i.star0,"x"]
      EU.star0 <- df.final0[i.star0, "EU"]
      EProf.star0 <- df.final0[i.star0, "EProf"]
      
    ## --- End risk-neutral case for for current parameter values -- ##

    ## Computing for all  values in r.list
    df.UMat <- map_df(df.profMat, U.CRRA, r = r.list[i.r])
    
    # Computing the integral
    df.EUMat <-  data.frame(mapply(`*` , df.UMat, Epsilons$probeps))
    df.final$EU <- rowSums(df.EUMat,  na.rm=T)

    # Computing the index of the maximum; storing maximum Expected Utility and profit
    i.star <- which.max(df.final$EU)
    x.star  <- df.final[i.star,"x"]
    EU.star <- df.final[i.star, "EU"]
    EProf.star <- df.final[i.star, "EProf"]
    
    # Share of input used for self-insurance
    delta.x <- 100*(x.star - x.star0)/x.star

    # Computing the risk premium
      ## -- Defining the optimization function
      fopti.CRRA.r <- function(RP, ...){
        abs(EU.star - U.CRRA(df.final[i.star,]$EProf - RP,r = r.list[i.r]))
      }

    # CRRA solution and risk premium
    RP.sol <- optimize( fopti.CRRA.r, interval = c(-100,500), maximum = FALSE)
    RP <- round(RP.sol$minimum, digits = 3)

    ###  Certainty equivalent
    CE <- df.final[i.star,"EProf"] - RP

    ## Putting results in data frame
    res.CRRA[ 1, paste0("r = ",r.list[i.r])] <- round(x.star, digits = 0)
    res.CRRA[ 2, paste0("r = ",r.list[i.r])] <-  round(delta.x, digits = 2)
    res.CRRA[ 3, paste0("r = ",r.list[i.r])] <-  round(RP, digits = 0)
    res.CRRA[ 4, paste0("r = ",r.list[i.r])] <-  round(-100*RP/EProf.star, digits = 2)
    res.CRRA[5, ] <- NA

  } #end loop over values of r

  rownames(res.CRRA) <- c( "X*","Input change", "RP","RP/Prof*", " " )

  # Appending the results for the next loop  
  Simu.prod.f  <-  rbind( Simu.prod.f , res.CRRA)

}  #end loop over mean production function parameters

## Formatted output
stargazer(Simu.prod.f,
          summary = FALSE,
          title = paste("Price ratio =", py,", Initial wealth = ", w0),
          notes = paste0("Production function = f(x) + ", param.prod.g,
                         " (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("Table3-", format(Sys.time(), "%Y-%m-%d")," .txt")
          )

```

# Simulation results: CPT framework


```{r BenchmarkEUNeutral, echo = FALSE}
# We need to compute some benchmark elements (EU framework) for future comparisons
py <- 11
# Initial wealth
w0 <- 500

# Production function parameters
c0 <- 0
a <- 15
alpha <- 0.30
b <- 30
beta <- -0.10

# Recording production function parameters information
text.param.prod <-  paste0("Production function y =", ifelse(c0 == 0, "",paste(c0,"+")),
                           a," * x**", alpha, " + ",b,"* x**",beta," * eps" )
text.param.prod2 <- paste("Price ratio =",py,", Initial wealth =", w0 )

####  Individual profit  ----

df.profMat0 <- data.frame(mapply(function(x, y)
  (w0 + py*(c0 + a * x^alpha + b * (x ^beta) *y) - x),
  df,Epsilons$eps))

## Computing the probabilistic profit

df.ProbProfMat0 <- data.frame(mapply(`*` , df.profMat0, Epsilons$probeps))
# Expected profit
df.ExpectedProf0 = rowSums(df.ProbProfMat0,  na.rm=T)

# Computing some reference values for base profit (to be used later)
prof.25 <- round(quantile(df.ExpectedProf0, probs = 0.25),0)
prof.50 <- round(quantile(df.ExpectedProf0, probs = 0.50),0)
prof.max <- round(max(df.ExpectedProf0),0)

```

## Optimal quantity of input used and risk premium under various CPT scenarios

```{r LoopCPT, echo = TRUE }
# Table 4 is constructed as a double loop: [values can be changed here]

# First Loop: 
# CPT scenarios definition
# Parameter values are (resp.): rr+, rr- ,lamda, gamma and delta
scenarios <-      data.frame(c(0.12,0.12,2.25, 0.61,0.69 )) #Scenario 0 (KT)
scenarios <- cbind(scenarios,c(0.12,0.12,2.25, 0.61,0.30 )) #Scenario 1
scenarios <- cbind(scenarios,c(0.88,0.12,2.25, 0.61,0.69 )) #Scenario 2
scenarios <- cbind(scenarios,c(0.88,0.12,2.25, 0.61,0.30 )) #Scenario 3
scenarios <- cbind(scenarios,c(0.88,0.12,3.50, 0.61,0.30 )) #Scenario 4

names(scenarios) <- c("KT", "Sc.1", "Sc.2", "Sc.3", "Sc.4")
row.names(scenarios) <- c("rr+", "rr-", "lambda", "gamma", "delta")

#Inner loop: Values considered for reference point, wref 
wref.list <- c(0, prof.50, prof.max)

```

**Table 4**


```{r Table4 , include = TRUE, echo = FALSE, cache = FALSE}

# Initializing results
results <- data.frame(matrix(ncol = ncol(scenarios),nrow = 2*length(wref.list),
                             dimnames=list(NULL, names(scenarios))))

##Looping over the scenarios (in column)
for (j in 1:ncol(scenarios) )  {
    # Current scenario index
    sc.num <- j

    # Inputting parameters for each scenario

    rrplus.input <-  scenarios[c("rr+"), sc.num]   # Scenario 0 is in column 1
    rrminus.input <- scenarios[c("rr-"), sc.num]
    lambda.input <-  scenarios[c("lambda"), sc.num]
    gamma.input <-   scenarios[c("gamma"), sc.num]
    delta.input <-   scenarios[c("delta"), sc.num]

    # Looping over the reference point values, wref
    for (i in seq_along(wref.list))  {

      ###  Reference point
      wref.input <-   wref.list[i]  
      text.param.KT <-  paste0("Ref. Point wref = ", wref.input)

      ##  Calling the CPT optimizing function with current parameters
      ## and using the Tversky and Kahneman (1992) value function

      results.KT <- resultsKT(df.profit = df.profMat0,
                                     # Reference point 
                                     wref = wref.input,
                                     # Curvature parameters
                                     rrplus = rrplus.input,
                                     rrminus = rrminus.input,
                                     # Degree of loss aversion
                                     lambda = lambda.input,
                                     # Decision weight  parameters
                                     delta = delta.input,
                                     gamma = gamma.input
                          )


     # Computing difference with the risk-neutral optimal input
      delta.x <- round(100*(results.KT$X.star - 264)/results.KT$X.star, 1)

     # Storing current loop results (two lines) in the data frame
      k <- 2*i -1
      results[k, sc.num ] <- paste0(results.KT$X.star," (",delta.x, "%)")
      results[k+1, sc.num ] <- paste0("[RP = ", round(results.KT$RP, 0), "]")

    }  # end loop cases (wref values)

} #end loop scenarios

# Storing the results in a formatted data.frame
Simu.Output <- rbind(scenarios, results)
row.names(Simu.Output) <- c(row.names(scenarios) ,
                            "x* (Ref = 0)", " -",
                            "x*(Ref = Median)", "- ",
                            "x* (Ref = Max)", " - ")

## Formatted output
values.profits <- paste(unlist(wref.list), collapse=', ')
stargazer(Simu.Output,
          summary = FALSE,
          title = paste0("CPT", text.param.prod2, ", Refs (0, med., max) = resp. ", values.profits),
          notes =  paste0(text.param.prod,"  (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("Table4-", format(Sys.time(), "%Y-%m-%d")," .txt")
          )


```

## Sensitivity of input use and risk premium to pesticides-crop price ratio – CPT framework

```{r loopPriceCPT, echo = TRUE}
# Table 5 is constructed as a double loop: [values can be changed here]

# First Loop: 
# CPT Scenarios definition
# -> We use here the same scenarios as in Table 4

# Inner loop: 
# Values considered for price ratio parameters
py.list <- c(11, 13, 7)

# We need here to recall the risk-neutral optimum for each price ratio (from Table 2)
x.star.py <-Simu.py %>% filter(`price ratio` %in% py.list) %>% select( `price ratio`,`r = 0`)

# Uncomment the next line to print the values of the risk-neutral optimum for each price ratio
# x.star.py
```

**Table 5**

```{r Table5 , include = TRUE, echo = FALSE, cache = FALSE}

# Initializing results in data frames
results.py <- data.frame(matrix(ncol = ncol(scenarios),nrow = 2*length(py.list),
                             dimnames=list(NULL, names(scenarios))))
prof.med.list <- ""


## Looping over the scenarios defined for Table 4
for (j in 1:ncol(scenarios) )  {
  # Current scenario number
  sc.num <- j

  # Inputting parameters for current scenario
  rrplus.input <-  scenarios[c("rr+"), sc.num]   
  rrminus.input <- scenarios[c("rr-"), sc.num]
  lambda.input <-  scenarios[c("lambda"), sc.num]
  gamma.input <-   scenarios[c("gamma"), sc.num]
  delta.input <-   scenarios[c("delta"), sc.num]

  # looping over price ratio, py
  for (i in seq_along(py.list)) {

    # Curent price ratio
    py <- py.list[i]
    # Current risk-neutral optimum X0* for current price ratio py
    x0.star.py <- x.star.py[which( x.star.py$`price ratio` == py),2]
    # Text for output 
    text.param.KT <-  paste0("Price ratio = ", py, " -RefX0 = ", x0.star.py )
    
    ####  Individual profit  ----
    df.profMat0 <- data.frame(mapply(function(x, y)
      (w0 + py*(c0 + a * x^alpha + b * (x ^beta) *y) - x),
      df,Epsilons$eps))

    ## Computing the probabilistic profit

    df.ProbProfMat0 <- data.frame(mapply(`*` , df.profMat0, Epsilons$probeps))
    # Expected profit
    df.ExpectedProf0 = rowSums(df.ProbProfMat0,  na.rm=T)

    # Computing the reference point (set at the median profit) for the current scenario and price ratio
    prof.med <- round(quantile(df.ExpectedProf0, probs = 0.50),0)

    # Recording the current values for text output
    prof.med.list <- ifelse(j == ncol(scenarios),paste0(prof.med.list, " ", prof.med), " ")

    ##  Calling the CPT optimizing function with current parameters
    ## and using the Tversky and Kahneman (1992) value function

    results.KT <- resultsKT(df.profit = df.profMat0,
                            # Reference point 
                            wref = prof.med,
                             # Curvature parameters
                            rrplus = rrplus.input,
                            rrminus = rrminus.input,
                            # Degree of loss aversion
                            lambda = lambda.input,
                            # Weight function parameters
                            delta = delta.input,
                            gamma = gamma.input
    )


    # Computing difference with the risk-neutral optimum
    delta.x <- round(100*(results.KT$X.star - x0.star.py)/results.KT$X.star, 1)

   
    # Storing current loop results (two lines) in the data frame
    k <- 2*i -1
    results.py[k, sc.num ] <- paste0(results.KT$X.star," (",delta.x, "%)")
    results.py[k+1, sc.num ] <- paste0("[RP = ", results.KT$RP, "]")

  }  # end loop cases (py values)
} #end loop scenarios

#### Results (in a data.frame) ###

Simu.Output.py <- rbind(scenarios, results.py)
row.names(Simu.Output.py) <- c(row.names(scenarios) ,
                               paste("x* (ratio 1-",py.list[1],")" ) , paste(" X0* ref. =", x.star.py[1, 1]),
                               paste("x* (ratio 1-",py.list[2],")" ) , paste(" X0* ref. =", x.star.py[2,1]),
                               paste("x* (ratio 1-",py.list[3],")" ) , paste(" X0* ref.=", x.star.py[3,1]))


## Formatted output
py.list.values <- paste(unlist(py.list), collapse=', ')

stargazer(Simu.Output.py,
          summary = FALSE,
          title = paste0("CPT: Initial wealth =", w0,
                         ", Ref.Point = med. profit (py = ", py.list.values,") = resp.",
                         prof.med.list ),
          notes =  paste0(text.param.prod," (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("Table5-", format(Sys.time(), "%Y-%m-%d")," .txt")
)


```


# Appendix

## Sensitivity of input use and risk premium to levels of relative risk aversion and parameters of the risk function (EU framework) 

```{r LoopG, echo=TRUE}
# Table A4 is constructed as a double loop: [values may be changed Here]

# First Loop: 
# Cases proposed for risk function parameters b and beta

case.prod.g <-       data.frame(c(20, -0.1))  # Case1
case.prod.g<- cbind(case.prod.g,c(40, -0.1))  # Case2
case.prod.g<- cbind(case.prod.g,c(30, -0.1 )) # Benchmark
case.prod.g<- cbind(case.prod.g,c(30, -0.2 )) # Case4

# NB: Mean production function parameters are fixed
C0 <- 0
a <- 15
alpha <- 0.30

# Inner loop: 
# risk aversion parameters as in Tables 1, 2 and 3
r.list <- c(0,1,2,3,4) 

# Invariant (in this simulation) parameters
w0 <- 500
py <- 11

```

**Table A4**

```{r  TableA4, include = TRUE, echo = FALSE, cache = FALSE}

# Initializing
Simu.prod.g <- data.frame()

for (j in 1:ncol(case.prod.g) )  {

  # Risk function parameters for the current case
  b = case.prod.g[1,j]
  beta = case.prod.g[2,j]

  # text for output table
  param.prod.f <- paste0(ifelse(c0 == 0, "",paste(c0," + ")), a,"* x**", alpha )
  param.prod.g <- paste0(b,"* x**",beta)
  text.param.prod <-  paste0("Production function y = ",param.prod.f," + ",param.prod.g,"* eps"  )

  #Individual profit
  df.profMat <- data.frame(mapply(function(x, y) (w0 + py*( c0 + a * x^alpha + b * (x ^beta) *y) - x),
                                  df,Epsilons$eps))

  # Computing the integral (expected profit)
  df.EprofMat <- data.frame(mapply(`*` , df.profMat, Epsilons$probeps))

  # Expected profit
  df.final$EProf <- rowSums(df.EprofMat,  na.rm=T)

  res.CRRA<- data.frame()
  # Loop over the risk parameters
  for (i.r in seq_along(r.list))  {
    res.CRRA [1, "Risk function"] <- paste0("g(x) = ",param.prod.g)

    ## --- Computing the risk-neutral optimum for that case -- ##
      # Initialisation
      df.final0 <- df    
      df.UMat0 <- map_df(df.profMat, U.CRRA, r = 0)
      
      # Computing the integral
      df.EUMat0 <-  data.frame(mapply(`*` , df.UMat0, Epsilons$probeps))
      df.final0$EU <- rowSums(df.EUMat0,  na.rm=T)
  

      # Computing the index of the maximum (r = 0 case)
      i.star0 <- which.max(df.final0$EU)
      x.star0  <- df.final0[i.star0,"x"]
      EU.star0 <- df.final0[i.star0, "EU"]
      EProf.star0 <- df.final0[i.star0, "EProf"]
      
    ## --- End risk-neutral case for that value of price ratio -- ##

    ## Computing for all r.list values
    df.UMat <- map_df(df.profMat, U.CRRA, r = r.list[i.r])
    # Computing the integral

    df.EUMat <-  data.frame(mapply(`*` , df.UMat, Epsilons$probeps))
    df.final$EU <- rowSums(df.EUMat,  na.rm=T)


    # Computing the index of the maximum; storing maximum Expected Utility and profit
    i.star <- which.max(df.final$EU)
    x.star  <- df.final[i.star,"x"]
    EU.star <- df.final[i.star, "EU"]
    EProf.star <- df.final[i.star, "EProf"]

    # Share of input used for self-insurance
    delta.x <- 100*(x.star - x.star0)/x.star

    # Computing risk premium
      ## -- Defining the optimization function for that case
    fopti.CRRA.r <- function(RP, ...){
      abs(EU.star - U.CRRA(df.final[i.star,]$EProf - RP,r = r.list[i.r]))
    }

    
    # CRRA solution and risk premium
    RP.sol <- optimize( fopti.CRRA.r, interval = c(-100,500), maximum = FALSE)
    RP <- round(RP.sol$minimum, digits = 3)

    ###  Certainty equivalent
    CE <- df.final[i.star,"EProf"] - RP

    ## Putting results in table for current risk parameter and risk function parameters
    res.CRRA[ 1, paste0("r = ",r.list[i.r])] <- round(x.star, digits = 0)
    res.CRRA[ 2, paste0("r = ",r.list[i.r])] <-  round(delta.x, digits = 2)
    res.CRRA[ 3, paste0("r = ",r.list[i.r])] <-  round(RP, digits = 0)
    res.CRRA[ 4, paste0("r = ",r.list[i.r])] <-  round(-100*RP/EProf.star, digits = 2)
    res.CRRA[5, ] <- NA

  } #end loop over risk aversion values, r

  rownames(res.CRRA) <- c( "X*","Input change", "RP","RP/Prof*", " " )


  # Appending the results for the next loop  
  Simu.prod.g  <-  rbind( Simu.prod.g , res.CRRA)

}  #end loop over risk function parameters, g()


## Formatted output
stargazer(Simu.prod.g,
          summary = FALSE,
          title = paste("Price ratio =", py,", Initial wealth = ", w0),
          notes = paste0("Production function =", param.prod.f,"+ g(x)*eps (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("TableA4-", format(Sys.time(), "%Y-%m-%d")," .txt")
          )

```

## Sensitivity to initial wealth


```{r LoopW0, echo=TRUE}
# Table A5 is constructed as a double loop: [values may be changed Here]

# First Loop: 
# Simulation values for initial wealth, w0:
w0.list <- c(500, 1000, 1500, 5000)

# Inner loop: 
# risk aversion parameters as in Tables 1, 2 and 3
r.list <- c(0,1,2,3,4)

#Invariant (in this simulation) parameters
#production function are as in Benchmark case
c0 <- 0
a <- 15
alpha <- 0.30
b <- 30
beta <- -0.10

#Price ratio
py <- 11
```


```{r TableA5, include = TRUE, echo = FALSE, cache = FALSE}
# Initializing 
Simu.w0 <- data.frame()


for (j in seq_along(w0.list))  {
  #initializing
  res.CRRA<- data.frame()
  
  # Profit function parameters
  w0 <- w0.list[j]   
  
  
  # text for output table
  param.prod.f <- paste0(ifelse(c0 == 0, "",paste(c0," + ")), a,"* x**", alpha )
  param.prod.g <- paste0(b,"* x**",beta)
  text.param.prod <-  paste0("Production function y = ",param.prod.f," + ",param.prod.g,"* eps"  )

  #Individual profit
  df.profMat <- data.frame(mapply(function(x, y) (w0 + py*( c0 + a * x^alpha + b * (x ^beta) *y) - x),
                                  df,Epsilons$eps))
  
  # Computing the integral  (Expected profit)
  df.EprofMat <- data.frame(mapply(`*` , df.profMat, Epsilons$probeps))
  
  # Expected Profit
  df.final$EProf <- rowSums(df.EprofMat,  na.rm=T)
  
  for (i.r in seq_along(r.list))  {
    res.CRRA [1, "Initial Wealth"] <- w0
    
     ## --- Computing the risk-neutral optimum for that price ratio -- ##
      #Initialization
      df.final0 <- df
      
      df.UMat0 <- map_df(df.profMat, U.CRRA, r = 0)
      # Computing the integral 
      
      df.EUMat0 <-  data.frame(mapply(`*` , df.UMat0, Epsilons$probeps))
      df.final0$EU <- rowSums(df.EUMat0,  na.rm=T)
      
      # Computing the index of the maximum (r = 0 case)
      i.star0 <- which.max(df.final0$EU)
      x.star0  <- df.final0[i.star0,"x"]
      EU.star0 <- df.final0[i.star0, "EU"]
      EProf.star0 <- df.final0[i.star0, "EProf"]
    ## --- End risk-neutral case for that value of price ratio -- ## 
    
    
    ## Computing for all  r.list values 
    df.UMat <- map_df(df.profMat, U.CRRA, r = r.list[i.r])
    
    # Computing the integral 
    df.EUMat <-  data.frame(mapply(`*` , df.UMat, Epsilons$probeps))
    df.final$EU <- rowSums(df.EUMat,  na.rm=T)
    
    # Computing the index of the maximum; storing maximum Expected Utility and profit
    i.star <- which.max(df.final$EU)
    x.star  <- df.final[i.star,"x"]
    EU.star <- df.final[i.star, "EU"]
    EProf.star <- df.final[i.star, "EProf"]
    
    # Share of input used for self-insurance
    delta.x <- 100*(x.star - x.star0)/x.star
    
     # Computing the risk premium
      ## -- Defining the optimization function for current value of r 
      fopti.CRRA.r <- function(RP, ...){
        abs(EU.star - U.CRRA(df.final[i.star,]$EProf - RP,r = r.list[i.r]))
      }
    
    # CRRA solution and Risk premium  
    RP.sol <- optimize( fopti.CRRA.r, interval = c(-100,500), maximum = FALSE)
    RP <- round(RP.sol$minimum, digits = 3)
    
    ###  Certainty equivalent
    CE <- df.final[i.star,"EProf"] - RP
    
    ## Puting results in table for current risk parameter and initial wealth values
    
    res.CRRA[ 1, paste0("r = ",r.list[i.r])] <- round(x.star, digits = 0)
    res.CRRA[ 2, paste0("r = ",r.list[i.r])] <-  round(delta.x, digits = 2)
    res.CRRA[ 3, paste0("r = ",r.list[i.r])] <-  round(RP, digits = 0)
    #res.CRRA[ 4, paste0("r = ",r.list[i.r])] <-  round(CE, digits = 0)
    res.CRRA[ 4, paste0("r = ",r.list[i.r])] <-  round(-100*RP/EProf.star, digits = 2)
    res.CRRA[5, ] <- NA
    
    rownames(res.CRRA) <- c( "X*","Input change", "RP","RP/Prof*", " " )
    
  } #end loop over values of r
  
  # Appending the results for the next loop
  Simu.w0 <-  rbind( Simu.w0, res.CRRA)
  
}  #end loop over initial wealth    

## formatted output 
stargazer(Simu.w0,
          summary = FALSE,
          title = paste("CRRA (N.eps =", N.eps,"), Price ratio = ", py),
          notes = paste0(text.param.prod,"  (Last run:", format(Sys.time(), "%Y-%m-%d"), ")"),
          digits = 1,
          type = 'text', out = paste0("TableA5-", format(Sys.time(), "%Y-%m-%d")," .txt")
)

```


